% ============================================================================
% BT#11 — PRL Letter  [LOCKED]
%
% Title: "A Conditional Landauer–Nelson Bridge
%         with Non-Markovian TICE Closure"
%
% Author: Kevin Henry Miller
% Target: Physical Review Letters (~3750 words core)
% Status: LOCKED — Submission-ready draft
% SHA-256: E5F4225DB05FB86B703D4163DB497E4F62AE40872C0021B7E9A6525EE6502DFA
% Lock date: 2026-03-18
%
% DELETED from this version:
%   "derived from first principles"
%   "forced uniquely by Bochner positivity"
%   "solved by Gödel/Floquet/singularity engine"
%
% KEPT:
%   conditional theorem
%   exact algebra
%   exact kernel-dependent closure forms
%   exact deviation law
% ============================================================================

\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb]{revtex4-2}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{xcolor}

% Shortcuts
\newcommand{\kB}{k_{\mathrm{B}}}
\newcommand{\Dth}{D_{\mathrm{th}}}
\newcommand{\Dq}{D_{\mathrm{q}}}
\newcommand{\geff}{\gamma_{\mathrm{eff}}}
\newcommand{\tcor}{\tau_{\mathrm{cor}}}
\newcommand{\Ebr}{E_{\mathrm{bridge}}}
\newcommand{\EL}{E_{\mathrm{Landauer}}}
\newcommand{\CTICE}{C_{\mathrm{TICE}}}

\begin{document}

\preprint{TICE-2026-001}

\title{A Conditional Landauer--Nelson Bridge\\
with Non-Markovian TICE Closure}

\author{Kevin Henry Miller}
\email{Kevin@qbondnetwork.com}
\homepage{https://www.qbondnetwork.com}
\affiliation{Founder and President, Q-Bond Network DeSCI DAO, LLC}
\noaffiliation
% ORCID: 0009-0007-7286-3373

\date{\today}

% ============================================================================
%  ABSTRACT — three parts: (1) exact theorem, (2) TICE embedding,
%  (3) what remains unproven
% ============================================================================
\begin{abstract}
% --- Part 1: exact theorem ---
We prove that five conditions are pairwise equivalent for a
quantum Brownian particle coupled to a thermal bath:
(i)~the thermal-to-quantum diffusion ratio is $\Dth/\Dq = 2$;
(ii)~the friction coefficient is $\gamma_0 = \kB T/\hbar$;
(iii)~the bath correlation time is $\tcor = \hbar/(\kB T)$;
(iv)~the bridge energy
$\Ebr \equiv \kB T \ln(\Dth/\Dq) = \kB T \ln 2$
equals one Landauer bit of erasure;
(v)~the ratio $\Dth/\Dq$ is temperature-independent.
Exact deviation formulas
$\Delta E = -\kB T\ln(1+\delta)$ are derived for departures
from this closure.
% --- Part 2: TICE embedding ---
We embed the result in a non-Markovian framework by introducing
a TICE closure factor $\CTICE(t) = \kB T/[\hbar\,\geff(t)]$
that generalizes the theorem to memory-kernel--dependent
effective friction, yielding
$\Ebr^{\mathrm{TICE}} = \kB T\ln(2\CTICE)$.
% --- Part 3: what remains unproven ---
The theorem is conditional on one postulate---that thermal
diffusion accounts for both time-directed noise channels in
Nelson's stochastic mechanics---which we motivate from five
independent physical contexts but do not derive from first
principles.
\end{abstract}

\maketitle

% ============================================================================
\section{Introduction}
% ============================================================================

Landauer's principle~\cite{Landauer1961} bounds the minimum cost
of irreversible bit erasure at $\EL = \kB T \ln 2$.
Nelson's stochastic mechanics~\cite{Nelson1966} ascribes to every
quantum particle a diffusion coefficient $\Dq = \hbar/(2m)$.
The Caldeira--Leggett model~\cite{CaldeiraLeggett1983} gives a
thermalized particle the diffusion $\Dth = \kB T/(m\gamma_0)$
via the fluctuation--dissipation theorem.

In this Letter we show that a single closure
condition---$\Dth = 2\Dq$---locks the friction to
$\gamma_0 = \kB T/\hbar$ and produces a bridge energy of
exactly one Landauer bit.  We state the theorem, prove it,
derive exact deviation formulas, embed it in a memory-kernel
framework, give one explicit kernel solution, and identify
three falsification protocols.  We are explicit throughout
about what is proven and what is postulated.

% ============================================================================
\section{Definitions}
% ============================================================================

Consider a quantum Brownian particle of mass $m$ coupled to
a heat bath at temperature $T$ through an Ohmic--Drude spectral
density
$J(\omega) = m\gamma_0\omega\,\Omega^2/(\omega^2 + \Omega^2)$,
where $\Omega$ is the Drude cutoff~\cite{CaldeiraLeggett1983}.
In the high-$T$ Markov regime ($\kB T \gg \hbar\Omega$) the
classical FDT gives $\Dth = \kB T/(m\gamma_0)$.

Define the \emph{diffusion ratio} and \emph{bridge energy}:
\begin{align}
  R &\equiv \frac{\Dth}{\Dq}
    = \frac{2\kB T}{\gamma_0 \hbar} ,
  \label{eq:R}\\
  \Ebr &\equiv \kB T \ln R
    = \kB T \ln\!\biggl(\frac{2\kB T}{\gamma_0\hbar}\biggr) .
  \label{eq:Ebr}
\end{align}
Both are manifestly independent of $m$.

% ============================================================================
\section{Equivalence Theorem}
% ============================================================================

\noindent\textbf{Theorem.}
\textit{The following five conditions are pairwise equivalent:}
\begin{enumerate}
  \item[(i)]   $\Dth = 2\Dq$.
  \item[(ii)]  $\gamma_0 = \kB T / \hbar$.
  \item[(iii)] $\tcor \equiv 1/\gamma_0 = \hbar / (\kB T)$.
  \item[(iv)]  $\Ebr = \kB T \ln 2 = \EL$.
  \item[(v)]   $\partial R/\partial T = 0$ at fixed $R$.
\end{enumerate}

\noindent\textit{Proof.}
(i)$\Leftrightarrow$(ii):
$\kB T/(m\gamma_0) = \hbar/m$ gives $\gamma_0 = \kB T/\hbar$.
(ii)$\Leftrightarrow$(iii): definition.
(ii)$\Rightarrow$(iv):
$\Ebr = \kB T\ln[2\kB T/(\kB T)] = \kB T\ln 2$.
(iv)$\Rightarrow$(ii):
$\kB T\ln[2\kB T/(\gamma_0\hbar)] = \kB T\ln 2$
implies $\gamma_0\hbar = \kB T$.
(v)$\Leftrightarrow$(ii):
$R = 2\kB T/(\gamma_0\hbar)$ is $T$-independent iff
$\gamma_0 \propto T$; combined with $R = 2$ this gives
$\gamma_0 = \kB T/\hbar$ uniquely. \hfill$\square$

\medskip
\noindent The content of (iv) is that the unique
$T$-independent closure produces a bridge energy of
\emph{exactly one Landauer bit}---unit information
erasure cost.

% ============================================================================
\section{Exact Deviation Formula}
% ============================================================================

Write $\gamma_0 = \gamma^*(1+\delta)$ with
$\gamma^* \equiv \kB T/\hbar$.  Then:
\begin{equation}
  R = \frac{2}{1+\delta},\qquad
  \Delta E \equiv \Ebr - \EL = -\kB T\ln(1+\delta).
  \label{eq:dev}
\end{equation}
This is \emph{exact}.  The sign encodes thermodynamics:
$\delta > 0$ (overdamped) $\Rightarrow$ $\Delta E < 0$
(sub-Landauer);
$\delta < 0$ (underdamped) $\Rightarrow$ $\Delta E > 0$
(super-Landauer).
The second law ($\Ebr \geq \EL$ for irreversible
erasure~\cite{Landauer1961,Bennett1982}) requires
$\delta \leq 0$ at equilibrium.

% ============================================================================
\section{Closure Condition and Chain of Inference}
% ============================================================================

The theorem rests on one postulate atop four layers of
established physics:

\smallskip
\noindent\textbf{Layer 1} (Caldeira--Leggett~\cite{CaldeiraLeggett1983}):
Ohmic--Drude bath $\Rightarrow$ noise kernel
$N(\tau) \simeq (m\kB T\gamma_0\Omega/\hbar)\,e^{-\Omega|\tau|}$.

\noindent\textbf{Layer 2} (KMS $\to$ FDT):
$\tilde{N}(\omega) = \coth(\hbar\omega/2\kB T)\,\tilde{D}(\omega)$
$\Rightarrow$ $N(\tau) = (\kB T/\hbar)\,\eta(\tau)$ at high~$T$.

\noindent\textbf{Layer 3} (Green--Kubo):
$\Dth = \kB T/(m\gamma_0)$.

\noindent\textbf{Layer 4} (Nelson~\cite{Nelson1966}):
$\Dq = \hbar/(2m)$.

\medskip
\noindent\textbf{Conjecture~1} (closure condition).
\textit{The thermal diffusion $\Dth$ accounts for both
time-directed noise channels in Nelson's bidirectional
stochastic mechanics, giving $\Dth = 2\Dq$.}

\medskip
\noindent Under Conjecture~1 the theorem follows algebraically.
The conjecture is \emph{motivated}---not proven---by five
observations:
(a)~Nelson's forward and backward SDEs contribute independent
noise of equal variance, summing to $2\Dq$;
(b)~the KMS thermal time $\hbar/(\kB T)$ coincides with
$\tcor = 1/\gamma^*$;
(c)~the Caldeira--Leggett high-$T$ friction scales as
$\kB T/\hbar$;
(d)~at $R = 2$ the bridge energy equals exactly one Landauer
bit---the minimum cost of erasing one bit of time-direction
information;
(e)~$R = 2$ is the unique value that is simultaneously
$T$-independent and matches Landauer.

% ============================================================================
\section{TICE Closure Factor and Kernel Example}
% ============================================================================

\subsection{Non-Markovian generalization}

Define the TICE closure factor
\begin{equation}
  \CTICE(t) \equiv \frac{\kB T}{\hbar\,\geff(t)},
  \qquad
  R(t) = 2\,\CTICE(t),
  \label{eq:CTICE}
\end{equation}
where $\geff(t)$ is the time-dependent effective friction
from a memory kernel $K(\tau)$:
\begin{equation}
  \geff(t) = \gamma_0 + \beta \int_0^t K(t-\tau)\,
  |\psi(\tau)|^2\,d\tau .
  \label{eq:geff}
\end{equation}
The master formula for the bridge energy becomes:
\begin{equation}
  \boxed{
  \Ebr^{\mathrm{TICE}}(t) = \kB T \ln\bigl(2\,\CTICE(t)\bigr)}
  \label{eq:master}
\end{equation}
$\CTICE = 1$: exact Landauer.
$\CTICE > 1$: super-Landauer (thermodynamically allowed
for reversible work extraction).
$\CTICE < 1$: sub-Landauer (forbidden by second law
for irreversible erasure).

\subsection{Ohmic--Drude kernel}

For $K(\tau) = A\,e^{-\Omega|\tau|}$ with $A = m\kB T\gamma_0\Omega/\hbar$
and coupling $\beta$:
\begin{equation}
  \geff(t) = \gamma_0 + \frac{\beta A}{\Omega}
  \bigl(1 - e^{-\Omega t}\bigr),
\end{equation}
so that $\CTICE(t) \to \kB T/[\hbar(\gamma_0 + \beta A/\Omega)]$
as $t \to \infty$.
The bridge energy converges to
$\Ebr^\infty = \kB T\ln[2\kB T/(\hbar\gamma_0 + \hbar\beta A/\Omega)]$,
and the crossing time $t^*$ at which
$\Ebr^{\mathrm{TICE}}(t^*) = \kB T\ln 2$ is:
\begin{equation}
  t^* = \frac{1}{\Omega}\ln\!\Biggl(
  \frac{\beta A/\Omega}
  {\gamma_0 + \beta A/\Omega - \kB T/\hbar}\Biggr),
\end{equation}
real and positive when $\gamma_0 < \kB T/\hbar < \gamma_0 + \beta A/\Omega$.

% ============================================================================
\section{Falsification}
% ============================================================================

Three tests can falsify Conjecture~1:

\begin{enumerate}
\item \emph{Diffusion-ratio measurement.}
At the thermal--quantum boundary (trapped ions,
optomechanical oscillators), measure $\Dth$ and $\Dq$
independently.
Prediction: $R = 2.000 \pm \epsilon$.
Rejection: $R \neq 2$ at $>3\sigma$.

\item \emph{Optimal-erasure friction.}
In colloidal Landauer erasure~\cite{Berut2012,Jun2014},
the effective damping at quasi-static optimal erasure
should satisfy $\geff = \kB T/\hbar$.
Rejection: $\geff \neq \kB T/\hbar$ at the Landauer bound.

\item \emph{Superfluid He-4 second-sound attenuation.}
Five-temperature sweep at $0.5$--$2.17$~K.
Prediction: $\Dth/\Dq = 2$ with $\gamma = \kB T/\hbar$.
This provides an overconstrained test (5 data points,
1 parameter).
\end{enumerate}

% ============================================================================
\section{What Is and Is Not Proven}
% ============================================================================

\textit{Proven:}
The equivalence of conditions (i)--(v) is exact algebra.
The deviation formula~\eqref{eq:dev} is exact.
The TICE embedding~\eqref{eq:master} with the closure
factor~\eqref{eq:CTICE} is exact for any admissible kernel.
No approximations beyond the Markov regime for the base
theorem, and the kernel framework extends to non-Markovian
dynamics.

\textit{Not proven:}
Conjecture~1 ($\Dth = 2\Dq$) is not derived from first
principles.  It is a closure condition motivated by five
independent physical observations but not forced by any
known axiom.
The Bochner positivity of the kernel guarantees
\emph{admissibility} (the kernel is a valid bath correlator)
but does not \emph{uniquely select} this kernel or this
closure.
Three routes toward a first-principles derivation exist:
(a)~a thermofield-double construction proving forward/backward
noise independence in open systems;
(b)~a Guerra--Morato variational argument~\cite{GuerraMorato1983}
connecting the Nelson action to Landauer cost;
(c)~direct experimental measurement of $R$.

% ============================================================================
\section{Conclusion}
% ============================================================================

A single closure condition---$\Dth = 2\Dq$, motivated by the
bidirectional structure of Nelson's stochastic mechanics---implies
$\gamma_0 = \kB T/\hbar$ and a bridge energy of exactly one
Landauer bit.  Five equivalent formulations, an exact deviation
law, a memory-kernel generalization with TICE closure factor, one
explicit kernel solution, and three falsification protocols are
provided.  The result is conditional, and we have stated the
single remaining assumption explicitly.

\begin{acknowledgments}
The author thanks the Q-Bond Research Engine for systematic
verification of all algebraic and numerical results.
\end{acknowledgments}

\begin{thebibliography}{20}

\bibitem{Landauer1961}
R.~Landauer,
IBM J. Res. Dev. \textbf{5}, 183 (1961).

\bibitem{Nelson1966}
E.~Nelson,
Phys. Rev. \textbf{150}, 1079 (1966).

\bibitem{CaldeiraLeggett1983}
A.~O. Caldeira and A.~J. Leggett,
Physica A \textbf{121}, 587 (1983).

\bibitem{Bennett1982}
C.~H. Bennett,
Int. J. Theor. Phys. \textbf{21}, 905 (1982).

\bibitem{Berut2012}
A.~B\'erut \textit{et al.},
Nature \textbf{483}, 187 (2012).

\bibitem{Jun2014}
Y.~Jun, M.~Gavrilov, and J.~Bechhoefer,
Phys. Rev. Lett. \textbf{113}, 190601 (2014).

\bibitem{GuerraMorato1983}
F.~Guerra and L.~M. Morato,
Phys. Rev. D \textbf{27}, 1774 (1983).

\end{thebibliography}

\end{document}
